Sample-efficient Reinforcement Learning \\ with Implicitly Quantized Representations

### 2024-02-01 paper/main.tex

\our has four parameterized components.
\begin{align}
&\text{Encoder: } & z_{t} &= e_{\theta} (s_{t}) \label{eq:encoder} \\
&\text{Dynamics: } & \hat{z}_{t+1} &= d_{\phi} (z_{t}, a_{t}) \label{eq:transition} \\
&\text{Value: } & q_{t} &= Q_{\psi} (z_{t}, a_{t}) \label{eq:value} \\
&\text{Policy: } & a_{t} &\sim \pi_{\eta} (z_{t}) , \label{eq:policy}
\end{align}
Note that unlike TCRL \citep{zhaoSimplifiedTemporalConsistency2023}, our transition model does
not predict the reward.

@@

>>>>

\our has four parameterized components.
\begin{align}
&\text{Encoder: } & z_{t} &= e_{\theta} (s_{t}) \label{eq:encoder} \\
&\text{Dynamics: } & \hat{z}_{t+1} &= d_{\phi} (z_{t}, a_{t}) \label{eq:transition} \\
&\text{Value: } & q_{t} &= Q_{\psi} (z_{t}, a_{t}) \label{eq:value} \\
&\text{Policy: } & a_{t} &\sim \pi_{\eta} (z_{t}) . \label{eq:policy}
\end{align}
Central to our method is the latent state $z_{t}$

\textbf{Bounding the latent space}
Typically the latent state $z_{t} \in \R^{d}$
However, in our work we bound the domain of the latent space, \ie $z_{t} \in [-L, L]^{d}$.

@@

Whilst our method resembles TCRL \citep{zhaoSimplifiedTemporalConsistency2023} it is important to note that
our transition model does not predict the reward.
As such, our method learns a task-agnostic representation.
